---
title: "Plot"
author: "Olga Leśkiewicz"
format:
  html:
    embed-resources: true
editor: visual
---

## Introduction

I did this plot in my last assignment, but I didn't use ggplot, so this week I done it again with the right library.

## Code

As always I start with installing necessary libraries and creating dataframes of vectors containing the data:

```{r}
#| echo: false
#Installing necessary libraries:
library(dplyr)
library(scales) #It allows us using label_wrap in next codeblock
library(tidyr)
library(ggplot2)

#Creating data frame with data:
my_data <- data.frame(
  chronic_conditions <- c("High blood pressure", "Arthritis", "Back problems", "Eye problems", "Heart disease", "Osteoporosis", "Diabetes", "Urinary incontinence"),
  the_percentage_65_or_older <- c(52.9, 43.4, 28.6, 27.9, 22.7, 18.1, 17.2, 11.7)
)
```

I used webpage: https://r-graph-gallery.com/color-palette-finder for choosing colors. They are part of pallet "Antique". After defining our colors we start plotting.\
Since my labels where overlapping I started looking for solutions to this problem.\
This webpage: <https://www.andrewheiss.com/blog/2022/06/23/long-labels-ggplot/> summarizes the available solutions and afer reading it I decided to use label_wrap from library scales

```{r}

#We define our colors
color <- c("#855C75FF", "#D9AF6BFF", "#AF6458FF", "#736F4CFF", 
           "#526A83FF", "#625377FF", "#68855CFF", "#9C9C5EFF")


#We start plotting 
ggplot(my_data, aes(x = chronic_conditions, y = the_percentage_65_or_older, fill = chronic_conditions)) +
  geom_col(show.legend = FALSE) +
  scale_x_discrete(labels = label_wrap(10))+ #this commeds breakes labels
  scale_fill_manual(values = color) + #we fill our columns with previously defined colors
  labs(
    x = "Chronic Condition", 
    y = "Percentage (65+ years old)",
    title = "Percentage of People 65+ years old with Chronic Conditions"
  ) +
  theme_minimal() 
  
```
